---
title: "GAMM_F23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mgcv)
```

Pipeline for GAMM
1. Average left and right pupil dilation
2. Lienar interpolation of blinks
2. Median filter (baseline-correction is optional in GAMM modeling (see 1.
van Rij J, Hendriks P, van Rijn H, Baayen RH, Wood SN. Analyzing the Time Course of Pupillometric Data. Trends in Hearing. 2019;23. doi:10.1177/2331216519832483 ))
1. Downsample the data

What is GAMM-- an extension of regression; estimates the relation between a dependent variable and a number of given predictors. Instead of forcing the relation between dependent variable and predictor to be linear, as is the case in typical linear regression, this relation is modeled as a smooth function

```{r sample data}
load(file='/Users/juanbalcazar/Downloads/pupil_S2_alignPronoun.rda')
```

## GAMM with mixed effects-- treat the participant as a variable quantity

```{r GAMM model, echo=FALSE}
model <- bam(Pupil ~ Condition + 
               s(Time, by = Condition, k =20)
             + s(Time, Subject, bs = 'fs', m =1)
             +s(Time, Item = bs ='fs', m =1)
             , data = dat, discrete = TRUE)
#factor smooths specified with 'fs'
#thus random smooths for Subjects and Items
```

#test for significance

1. visual inspection of the model’s estimates of the differences between the conditions
2. a model-comparison procedure
3. inspection of the model summary statistics to determine the differences between conditions. 

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
