---
title: "Anxiety Depression Analyses"
author: "Juan Balcazar"
date: "11/7/2023"
output: html_document
---

```{r library, include=FALSE}
library(dplyr)
library(data.table)
library(ggplot2)
library(tidyverse)
library(brms)
library(car)
library(tidyverse)
library(brms)
library(datarium)
library(ggplot2)
library(dplyr)
library(ez)
library(pander)
library(knitr)
library(lme4)
library(sjPlot)
```


```{r pre-processing script, include=FALSE}
setwd("/Users/juanbalcazar/Library/CloudStorage/GoogleDrive-balc557@tamu.edu/Shared drives/VTSRewardExpectancy/data/vts_reward_mood_f23_pilot")
#read in file
filelist<-list.files(pattern="*csv")

fulldata <- data.frame()
for (file in filelist) {
  rawdata <- fread(file)    #added block
  data <- rawdata %>% select(participant, acc, E1, trialNum, blocks.thisRepN, blocks.thisN, trialNum_cumul, curr_leftStim, curr_rightStim,
                             alt, task, condition, target_resp.keys,
                             target_resp.rt, rewCond, points_trial, points_cumul,) 
  data$rewCond <-as.character(data$rewCond)
  data$RT <- as.numeric(data$target_resp.rt)
  data$RT <- data$RT * 1000 # convert from sec to ms  
  data$trial <- as.numeric(data$trialNum)
  data <- data %>% filter(!is.na(RT))

  # deterministic reward transition (EEG_ET)
  # rewCond 1 is no reward
  #rewCond 2 is low reward (response contingent)
  #rewCond 3 is high reward
  data$rewTrans=NA
  data <- data %>% 
    mutate(rewTrans = ifelse(trial>0 & rewCond=="Lo" & lag(rewCond)=="Lo", "remainLo",
                             ifelse(trial>0 & rewCond=="Hi" & lag(rewCond)=="Hi","remainHi", 
                                    ifelse(trial>0 & rewCond=="Hi" & lag(rewCond)=="Lo","increase",
                                           ifelse(trial>0 & rewCond=="Lo" & lag(rewCond)=="Hi","decrease",NA)))))

data$participant <- as.character(data$participant)  
#macmini home  
filename=sprintf("/Users/juanbalcazar/Library/CloudStorage/GoogleDrive-balc557@tamu.edu/Shared drives/VTSRewardExpectancy/data/vts_reward_mood_f23_pilot/parsed_data/%s_vts_reward_mood_pilot.csv", data$participant[1])
 # this will output  files to GDrive
  write.csv(data, filename)
  fulldata <- rbind(fulldata,data)
}

```


```{r read and analyze, include=TRUE}

#read in parsed data from Google Drive (behavioral parsed) to analyze behaiorals:VSR and switch costs
workdir ="/Users/juanbalcazar/Library/CloudStorage/GoogleDrive-balc557@tamu.edu/Shared drives/VTSRewardExpectancy/data/vts_reward_mood_f23_pilot/"
filelist<- Sys.glob(file.path(workdir,"parsed_data","*.csv")) #this need to have ID columns
fulldata <- data.frame()
for (file in filelist) {
  rawdata <- fread(file) 
  data <- rawdata %>% select (participant, blocks.thisRepN, blocks.thisN, trialNum_cumul, trialNum, curr_leftStim, curr_rightStim, alt, acc, E1, rewCond, points_trial, points_cumul, RT, rewTrans) 

  fulldata <- rbind(fulldata,data)
}
Behavioral_AnxietyDepress<- fulldata #rename for easier identification

#keep only trials that are reward blocks, this will also remove the first trial for each participant
Behavioral_AnxietyDepress<- Behavioral_AnxietyDepress[!Behavioral_AnxietyDepress$rewTrans =="NA", ] 

```

```{r conditions of interest}
#previous Condition
Behavioral_AnxietyDepress <- Behavioral_AnxietyDepress %>% 
  group_by(participant) %>% #important
  mutate(prevCondition = ifelse(trialNum_cumul>0 & lag(rewCond)=="Lo", "prev Lo",
                           ifelse(trialNum_cumul>0 & lag(rewCond)=="Hi","prev Hi",NA)))



Behavioral_AnxietyDepress <- Behavioral_AnxietyDepress %>%
mutate (Outcome = case_when(
  points_trial== 1 ~ "Low Correct", 
  points_trial== 10 ~ "High Correct",
  points_trial== 0 ~ "No Points",
  points_trial== -5 ~ "Loss",
  TRUE ~ as.character(NA)
)
)

#previous Outcome
Behavioral_AnxietyDepress <- Behavioral_AnxietyDepress %>% 
  group_by(participant) %>% #important
  mutate(prevOutcome = ifelse(trialNum_cumul>0 & lag(Outcome)=="Low Correct", "Prev Low Correct",
                           ifelse(trialNum_cumul>0 & lag(Outcome)=="High Correct","Previous High Correct",
                                  ifelse(trialNum_cumul>0 & lag(Outcome)=="No Points","Previous No Points",
                                         ifelse(trialNum_cumul>0 & lag(Outcome)=="Loss","Previous Loss",
                                  NA)))))
library(tidyr)
#Behavioral_AnxietyDepress %>% drop_na()
unique(Behavioral_AnxietyDepress$points_trial)
testLossProp <- filter(Behavioral_AnxietyDepress, points_trial== -5) #dataset
#for only losses

```

#LOAD anxieyt-depression measures

```{r}
Anxiety_Depres <- fread(file = "/Users/juanbalcazar/Documents/GitHub/F23_Anxiety Depression/prepped_VTSMoodPilot_DATA_LABELS_2024-10-04_0933.csv")

```


#no reverse scored items on the short form STAI. therefore continue

#find mean and median for state and trait scores

```{r}
#average across state
 Anxiety_Depres$MeanState_STAI <- rowMeans (subset (Anxiety_Depres,select = c("STAI_Upset", "STAI__FeelFrightened",
                            "STAI_FeelNervous","STAI_Feel_Jitter",
                            "STAI_FeelConfused")), na.rm = TRUE)

#average across TRAIT
 Anxiety_Depres$MeanTrait_STAI <- rowMeans (subset (Anxiety_Depres,select = c("STAI_FeelPilingUp", "STAI_WorryTooMuch",
                            "STAI_ThoughtsRun","STAI_KeenDisapointment",
                            "STAI_Turmoil")), na.rm = TRUE)
```

#median split into low anxiety and high anxiety
#the median is 2 from summary(Anxiety_Depres$MeanTrait_STAI)
```{r}
Anxiety_Depres <- Anxiety_Depres %>%
mutate (AnxietyGrp = case_when(
  MeanTrait_STAI > 2.00 ~ "High Anxiety", 
  MeanTrait_STAI < 2.00 ~ "Low Anxiety",
  TRUE ~ as.character(NA)
)
)
```


# use the normative mean of 50 for PROMIS depression
```{r}
Anxiety_Depres <- Anxiety_Depres %>%
mutate (DepresGroup = case_when(
  `T-score` > 50.0 ~ "High Depression", 
  `T-score` < 50.0 ~ "Low Depression",
  TRUE ~ as.character(NA)
)
)
```

#mean center anxiety
Mean centering is preferred when showing interactions
```{r}
Anxiety_Depres$meanCenterTraitAnx <- 
  scale(Anxiety_Depres$MeanTrait_STAI, center = TRUE, scale = FALSE)

```


```{r}
#select only the columns we need so that combining is faster
Anxiety_Depres <- Anxiety_Depres %>%
  select(`Participant ID`,`T-score`,`Standard Error`, `Complete?`, MeanTrait_STAI, 
         AnxietyGrp, DepresGroup, meanCenterTraitAnx)

#rename columns for clarity
new_names <- c("participant", "Depress_TScore", "Depress_SE", "Complete", "MeanTrait_STAI", "AnxietyGrp",
               "DepressGrp", "meanCenterTraitAnx")

names(Anxiety_Depres) <- new_names
```


```{r prepping the data}
library(dplyr)
sapply(Anxiety_Depres, function(x) sum(is.na(x)))
#remove 11 Anxiety NAs
Anxiety_Depres <- Anxiety_Depres[!is.na(Anxiety_Depres$AnxietyGrp),]

sapply(Behavioral_AnxietyDepress, function(x) sum(is.na(x)))
#remove an empty participant
Behavioral_AnxietyDepress <- Behavioral_AnxietyDepress[!is.na(Behavioral_AnxietyDepress$participant),]
Behavioral_AnxietyDepress <- Behavioral_AnxietyDepress[!is.na(Behavioral_AnxietyDepress$prevCondition),]
Behavioral_AnxietyDepress <- Behavioral_AnxietyDepress[!is.na(Behavioral_AnxietyDepress$prevOutcome),]

#remove Nas 


```

#combine anxiety,depression measures with behavior via ID
```{r}
#integrate rich behav data with anxiety and depression
Behavioral_AnxietyDepress$participant <- as.character(Behavioral_AnxietyDepress$participant) #as character
Anxiety_Depres$participant <- as.character(Anxiety_Depres$participant) # as character
conjoinedBehav_AnxDepres <- left_join(Behavioral_AnxietyDepress, Anxiety_Depres,
                          by = c("participant"))

sapply(conjoinedBehav_AnxDepres, function(x) sum(is.na(x)))

#remove NAs that are caused when joining anxiety/depression scores to an ID that does not exist
conjoinedBehav_AnxDepres <-
conjoinedBehav_AnxDepres[!is.na(conjoinedBehav_AnxDepres$AnxietyGrp),]

```


```{r VSR by reward transition, echo=FALSE}
Behavioral_AnxietyDepress<- Behavioral_AnxietyDepress[!Behavioral_AnxietyDepress$prevOutcome == "Previous Loss", ]

#Behavioral_AnxietyDepress<- Behavioral_AnxietyDepress[!Behavioral_AnxietyDepress$participant == "1004", ] 
#delete  NAS
Behavioral_AnxietyDepress <- na.omit(Behavioral_AnxietyDepress)

#VSR 
summary_VSR_RewTrans<- Behavioral_AnxietyDepress %>% group_by(participant, rewTrans, alt, prevOutcome) %>%
  dplyr::summarise(n=n()) %>%
  ungroup() %>%
  complete(participant, rewTrans, alt, fill = list(n = 0)) %>% # fill any missing cells
  group_by(participant) %>%
 # filter(!any(n < 3)) %>% # drop participants that have less than 5 counts in any cell
  group_by(participant, prevOutcome) %>%
  dplyr::summarise(VSR = sum(n[alt=="switch"])/sum(n), count=sum(n))


 summary_VSR_RewTrans <- summary_VSR_RewTrans[complete.cases(summary_VSR_RewTrans[ , c('prevOutcome', 'VSR')]), ]             

#remove previous loss and 

boxplot <-
summary_VSR_RewTrans %>% ggplot(aes(x= prevOutcome, y=VSR)) +
                geom_boxplot() +
                facet_grid(.~participant)
```


Prep variables

```{r linear mixed model regression, echo=FALSE}
#no test-train splitting;I do not think you need to divide the set if you are interested in the significance of a coefficient and not in prediction. 

conjoinedBehav_AnxDepres$altBinomial <- ifelse(conjoinedBehav_AnxDepres$alt == "switch", 1, 0)
conjoinedBehav_AnxDepres

library(sjlabelled)
set_label(conjoinedBehav_AnxDepres$altBinomial) <- "Probability of a Switch"

#factor your categorical variables
conjoinedBehav_AnxDepres$blocks.thisN = as.factor(conjoinedBehav_AnxDepres$blocks.thisN) 
conjoinedBehav_AnxDepres$AnxietyGrp = as.factor(conjoinedBehav_AnxDepres$AnxietyGrp)
conjoinedBehav_AnxDepres$DepressGrp = as.factor(conjoinedBehav_AnxDepres$DepressGrp)
conjoinedBehav_AnxDepres$prevOutcome = as.factor(conjoinedBehav_AnxDepres$prevOutcome)
conjoinedBehav_AnxDepres$prevCondition = as.factor(conjoinedBehav_AnxDepres$prevCondition)
conjoinedBehav_AnxDepres$rewCond = as.factor(conjoinedBehav_AnxDepres$rewCond)
conjoinedBehav_AnxDepres$participant = as.factor(conjoinedBehav_AnxDepres$participant)
```

#relevel
```{r}

conjoinedBehav_AnxDepres = conjoinedBehav_AnxDepres %>% 
  mutate(AnxietyGrp = relevel(AnxietyGrp, 1))
conjoinedBehav_AnxDepres = conjoinedBehav_AnxDepres %>% 
  mutate(DepressGrp = relevel(DepressGrp, 2))
```

Check the structure of the dataset
```{r}
#reduce to columns of interest
conjoinedBehav_AnxDepres <- conjoinedBehav_AnxDepres %>%
  select(altBinomial, participant, blocks.thisN , AnxietyGrp, DepressGrp, prevOutcome,
         prevCondition, rewCond, meanCenterTraitAnx, Depress_TScore)

#checck structure of data
str(conjoinedBehav_AnxDepres)
xtabs(~altBinomial + AnxietyGrp, data = conjoinedBehav_AnxDepres )
xtabs(~altBinomial + DepressGrp, data = conjoinedBehav_AnxDepres )

```



```{r}
library(flexplot)
flexplot(altBinomial~ Depress_TScore | meanCenterTraitAnx, data = conjoinedBehav_AnxDepres,
         method = "logistic", ghost.line = "grey", SE = TRUE, ghost.reference = )
```
GLMM, binomial family
Syntax
model = glmer(target ~ fixed1 + fixed2+  (1|random1) +  (1|random2), data=data)

#you will get as many n-1 coefficients as you have levels for that variable
#the first level of that variable is treated as the 'reference'
#the log odds of switching increase/decrease by ____(estimate) as we go from the reference
#to that level

#I removed blocks and it now converges well
```{r linear mixed model regression, echo=FALSE}
#mixed effects generalized linear model, response variable binomial
M1 <- glmer(altBinomial ~  AnxietyGrp + prevOutcome * DepressGrp + prevCondition + rewCond 
            + (1|participant), data = conjoinedBehav_AnxDepres, family = binomial(link = "logit"), na.action = na.omit)
summary(M1)

```

#table
```{r}
tab_model(M1)
```

```{r}
car::vif(M1) #values above 5 suggest multicollinearity
```

```{r}

```


```{r ICC variance, random effect, echo=FALSE}
#calculate ICC variance explained by the random effect
library(performance)
icc(M1, by_group = TRUE)
```

To interpet a negative odds ratio, simply take 1 dvidied by odds ratio and then 
interpret as "less likely to switch"
#list of exponentiated coefficients (i.e. odds ratios)
```{r}
Coeff <-
coef(M1)

#Odds ratios and confidence intervals for odds ratios
exp(cbind(AnxietyGrp=coef(M1)))

exp(Coeff)
```


#Plot random efects

```{r random effects, echo=FALSE}
#By default, plot_model() automatically exponentiates coefficients, if appropriate (e.g. for models with log or logit link). 
#eponentiated coefficeints are the odds ratios
library(glmmTMB)
library(sjPlot)
plot_model(M1, type = "re", show.values = FALSE, value.offset = 2, vline.color = "black") #plots the exponnentiated regression estimates (odds ratio)

#probability transform
plot_model(M1,type ="re", transform = "plogis", show.values = FALSE,
           vline.color = "black") #probaility transform for re
```

#plot Probabilities fixed effects
#plogis = transformed to probability
To plot only certain coefficients: # remove coefficients sex2, dep2 and dep3
plot_model(m1, rm.terms = c("sex2", "dep2", "dep3"))

#if this plot is too complicated, remove the interaction term

```{r probabilities for fixed effects, echo=FALSE}
plot_model(M1, type = "est", transform = "plogis", vline.color = "red", show.values = TRUE, value.offset = 0.40,value.size = 2.5, sort.est = TRUE)
```

univariate probabilities
Predicted values (marginal effects) for specific model terms. 
```{r linear, echo=FALSE}
#specify which terms to plot, predicted values(marginal effects)
plot_model(M1, type = "pred", terms = c("prevCondition"))
plot_model(M1, type = "pred", terms = c("prevOutcome"))
plot_model(M1, type = "pred", terms = c("blocks.thisN"))
plot_model(M1, type = "pred", terms = c("DepressGrp"))
plot_model(M1, type = "pred", terms = c("DepressGrp", "prevOutcome"))
plot_model(M1, type = "pred", terms = c("AnxietyGrp", "prevOutcome"))

plot_model (M1, type = "int") #automatic plotting of interaction model terms

plot_model(M1, type = "diag")#diagnostic, For generalized linear mixed models, returns the QQ-plot for random effects
```


```{r linear, echo=FALSE}
ranef(M1)$participant 

op <- options(digits = 4)
ranef(M1, drop = TRUE)
options(op)


```


```{r outliers and distributions, include=TRUE}

#check for RT outliers
cleanRTdata <- filter(Behavioral_AnxietyDepress, RT>200 & acc==1 & E1==0) #summary of RT

summary_RT <- cleanRTdata %>% 
  group_by(participant) %>%
  summarise(meanRT = mean(RT, na.rm = TRUE),
            logRT = log10(mean(RT, na.rm = TRUE)),
            sdRT = sd(RT, na.rm = TRUE),
            count = n())
summary(summary_RT)

#histogram overall RT
library(ggplot2)
ggplot(summary_RT, aes(x=meanRT)) + 
  geom_histogram(binwidth=50) +
  geom_vline(aes(xintercept=mean(meanRT)),color="blue", linetype="dashed", size=1) +
  scale_x_continuous(name="Mean RT", breaks = seq(400,1200,200)) +
  scale_y_continuous(name = "Count", breaks = seq(0,12,1)) + theme_classic()

# RT outliers
library(rstatix)
summary_RT %>% identify_outliers(meanRT) #1003 is an outlier but not extreme


#exclude any outliers
#BehavioralRich_F21_EEG_ET<- BehavioralRich_F21_EEG_ET[!BehavioralRich_F21_EEG_ET$participant =="1065", ] 
#BehavioralRich_F21_EEG_ET<- BehavioralRich_F21_EEG_ET[!BehavioralRich_F21_EEG_ET$participant =="1097", ] 

#acc outliers
summary_ACC <- Behavioral_AnxietyDepress %>% 
  group_by(participant) %>% 
  summarise(ACC = mean(acc, na.rm = TRUE), asinACC = asin(sqrt((mean(acc, na.rm = TRUE)))), count=sum(n()))
summary(summary_ACC)
summary_ACC %>% identify_outliers(ACC)
lowACC <- summary_ACC %>% 
  group_by(participant) %>% 
  filter(ACC<.68)

#excludeSubjs <- append(excludeSubjs,lowACC$participant)
#excludeSubjs <- excludeSubjs[!duplicated(excludeSubjs)]

#plot accuracy 
summary_ACC <- summary_ACC %>%
  group_by(participant) %>% 
  filter(ACC > .68)
ggplot(summary_ACC, aes(x=asinACC)) + 
  geom_histogram(binwidth=.01) + 
  geom_vline(aes(xintercept=mean(asinACC)),color="blue", linetype="dashed", size=1) +
  scale_x_log10(name="Asin Accuracy", breaks = seq(.8, 1.4, .05)) +
  scale_y_continuous(name = "Count", breaks = seq(0,10,1)) + theme_classic()


## Check for task choice distribution (letter vs. number task)
#Task choice is calculated as letter proportion, so 0% represents 100% number task choice
summary_task_choice <- fulldata %>%
  group_by(participant, alt) %>% 
  summarise(n = n()) %>% 
  group_by(participant) %>% 
 # filter(!participant %in% excludeSubjs) %>% 
  summarise(lettProp = sum(n[alt=="letter"])/sum(n))
summary(summary_task_choice)

#histogram of task choice
ggplot(summary_task_choice, aes(x=lettProp)) + 
  geom_histogram(binwidth=.01) + 
  geom_vline(aes(xintercept=mean(lettProp)),color="blue", linetype="dashed", size=1) +
  scale_x_continuous(name="Letter Task Proportion", breaks = seq(.3, .7, .05)) +
  scale_y_continuous(name = "Count", breaks = seq(0,20,2)) + 
  theme_classic()


#violin plot of task choice
ggplot(summary_task_choice, aes(x="",lettProp)) + 
  geom_violin(scale = "count") +
  geom_boxplot(width=.1,color = "blue", fill="light gray") +
  labs(
    x = NULL, y = "proportion of letter task"
  )

#check for task choice outliers
summary_task_choice %>% identify_outliers(lettProp) #none identified

#exclude subjects(if any)
#excludeSubjs <- append(excludeSubjs, c(93929,94377))
#excludeSubjs <- excludeSubjs[!duplicated(excludeSubjs)]

#summary task without outliers
summary_task_choice %>% group_by(participant) %>%  
  #filter(!participant %in% excludeSubjs) %>% 
  ggplot(aes(x="",lettProp)) + 
  scale_y_continuous(name = "Count", breaks = seq(.1,.7,.05)) +
  geom_violin(scale = "count") +
  geom_boxplot(width=.1,color = "blue", fill="light gray") +
  labs(x = NULL, y = "proportion of letter task"
  )

#VSR outlier
summary_VSR <- Behavioral_AnxietyDepress %>% 
  group_by(participant, alt) %>% 
  summarise(n=n()) %>% 
  group_by(participant) %>%
  summarise(VSR = sum(n[alt=="switch"])/sum(n))
summary(summary_VSR) 

#check for VSR outlier
summary_VSR %>% identify_outliers(VSR)
#no outliers reported
```

```{r analyses}

#VSR by RewardTransition
summary_VSR_RewTrans<- Behavioral_AnxietyDepress %>% group_by(participant, rewTrans, alt) %>%
  dplyr::summarise(n=n()) %>%
  ungroup() %>%
  complete(participant, rewTrans, alt, fill = list(n = 0)) %>% # fill any missing cells
  group_by(participant) %>%
 # filter(!any(n < 3)) %>% # drop participants that have less than 5 counts in any cell
  group_by(participant, rewTrans) %>%
  dplyr::summarise(VSR = sum(n[alt=="switch"])/sum(n), count=sum(n))


#pivot for jamovi
PivotJamoviVSR <-
  pivot_wider(
    summary_VSR_RewTrans,
    id_cols = participant,
    names_from = rewTrans,
    values_from = VSR,
  )

#write
fwrite(PivotJamoviVSR, "/Users/juanbalcazar/Documents/GitHub/EyeTracking_and_Gaze/VTSMood_VSR_RewTrans.csv")


#RT by PrevOutcome and Task

Behavioral_AnxietyDepress<- Behavioral_AnxietyDepress[!Behavioral_AnxietyDepress$prevOutcome == "Previous Loss", ]

summary_RT_AltPrevOutcome <- Behavioral_AnxietyDepress %>% 
  group_by(participant) %>%  
  group_by(participant, alt, prevOutcome) %>% 
  dplyr::summarize(RT = mean(RT, na.rm = TRUE), count = n()) %>%
  ungroup() %>%
  complete(participant, alt, prevOutcome, fill = list(count = 0, RT = NA))

#remove cases that 
summary_RT_AltRewCond <- summary_RT_AltRewCond %>% 
  group_by(participant) %>% filter(!any(count < 5))

#remove previous loss cases, since there are too few
summary_RT_AltPrevOutcome<- summary_RT_AltPrevOutcome[!summary_RT_AltPrevOutcome$prevOutcome == "Previous Loss", ]

#summarize for jamovi
PivotJamovi <-
  pivot_wider(
    summary_RT_AltPrevOutcome,
    id_cols = participant,
    names_from = c(alt,prevOutcome),
    values_from = RT,
  )

fwrite(PivotJamovi, "/Users/juanbalcazar/Documents/GitHub/Anxiety Depression Pilot/Anxiety_Depress_RT_Alt_PrevOutcome.csv")


# find means and sems for error bars
library(Rmisc)
library(pander)
sum <- summarySEwithin(summary_RT_AltPrevOutcome, measurevar="RT", withinvars=c("alt","prevOutcome"), idvar="participant")
sum %>%
  pander(caption='Output')

#graph RT with rewCond
library(ggplot2)
library(ggthemes)
cbPalette <- c("firebrick4", "blue1")
(plotH <-sum %>%  #pipe the summarized data 'sum'
    ggplot() +
    aes(x = rewCond, group = alt, y = RT, color = alt) +
    geom_line(size=1) +  
    scale_linetype_manual(values=c("solid", "solid"))+
    geom_text(aes(y = RT, label = round(RT)), position=position_dodge(width=0.6), size = 5.5)+
    geom_point(size=3, fill="white") +         
    geom_errorbar(data=sum, mapping=aes(x=rewCond, ymin=RT-se, ymax=RT+se), width=0.1, size=.7, color="black", position=position_dodge(width=0.0)) +
    scale_color_manual(values=cbPalette) +
    theme_hc(base_size = 17, base_family = "sans", style = c("default", "darkunica")) +
    theme(
      axis.title.y = element_text(vjust= 1.8, size = 18),
      axis.title.x = element_text(vjust= -0.5, face="bold.italic", size = 18),
      axis.title = element_text(face = "bold"),
      plot.title = element_text(color="black", size=16, face="bold.italic"),
      axis.text=element_text(size=15, face = "bold"),
      legend.position = c(0.9, 0.2),
      legend.background = element_rect(fill="lightblue",
                                       size=0.5, linetype="solid", 
                                       colour ="darkblue"),
      legend.title = element_text(colour="black", size=15, face="bold")) )
plotH+ scale_y_continuous(breaks=seq(600:640*10)) #increment y-axis marker by 10
plotH+labs(title="EEG-ET: Effect of Task: F(1,41) = 17.01, p <.001 \n Effect of Reward Condition: F(1,41) = 34.7, p <.001 \n
           Interaction was non-significant", 
           x="Reward Condition", y = "Reaction Time in Milliseconds") 



#Gathers SE for Bar plot's error bars, VSR
library(Rmisc)
#we want correct SE so use summary within
sumRewTranz_VSR <- summarySEwithin(summary_VSR_RewTrans, measurevar="VSR", withinvars=c("rewTrans"), idvar="participant")
sumRewTranz_VSR %>%
  pander(caption='Output')


#library(ggplot2); theme_set(theme_bw())
library(ggplot2)
library(ggthemes)
cbPalette <- c("deepskyblue", "orange","green", "red")
plotD<- ggplot(sumRewTranz_VSR, aes(x=rewTrans, 
                                    y=VSR, 
                                    color=rewTrans)) + 
  #geom_text(aes(y = VSR, label = round(VSR, 3)), color="black", position=position_dodge(width=0.9), vjust=-.8, hjust= 1.2, size=5, fontface = "bold")+
  geom_col( aes (fill = rewTrans), color="black", width = 0.6, size = 1.5, 
            position=position_dodge(.9)) +
  geom_errorbar(aes(ymin=VSR-se, 
                    ymax=VSR+se), 
                width=.1, color ='purple', size= .7, position=position_dodge(0.9)) +
  # ylim(.2, .5) +
  theme_hc(base_size = 21, base_family = "sans", style = c("default", "darkunica"))+
  theme(
    axis.title.y = element_text(vjust= 1.8),
    axis.text.x = element_blank(),
    legend.position = "right",
    plot.title = element_text(color="black", size=23, face="bold.italic"))+
  scale_fill_manual(values=cbPalette, labels = c("Decrease", "Increase", "Remain High", "Remain Low") )+ 
  labs (fill ="Levels of \n Reward Transition") +
  guides(color = FALSE) 

plotD + coord_cartesian(ylim=c(.2, .5)) + ggtitle("") +
  ylab("VSR, proportion of switches vs. total") + xlab(" ") #remove x-axis text


```


```{r}

summary_RT_AltRewCond <- BehavioralRich_F21_EEG_ET %>% 
  group_by(participant) %>%  
  group_by(participant, alt, rewCond) %>% 
  summarize(RT = mean(RT, na.rm = TRUE), count = n()) %>%
  ungroup() %>%
  complete(participant, alt, rewCond, fill = list(count = 0, RT = NA))

#remove 'the -1' from alt column
summary_RT_AltRewCond<- summary_RT_AltRewCond[!summary_RT_AltRewCond$alt == "-1", ] 

#remove cases that 
summary_RT_AltRewCond <- summary_RT_AltRewCond %>% 
  group_by(participant) %>% filter(!any(count < 5))

library(Rmisc)
library(pander)
sum <- summarySEwithin(summary_RT_AltRewCond, measurevar="RT", withinvars=c("alt","rewCond"), idvar="participant")
sum %>%
  pander(caption='Output')

#graph RT with rewCond
library(ggplot2)
library(ggthemes)
cbPalette <- c("firebrick4", "blue1")
(plotH <-sum %>%  #pipe the summarized data 'sum'
    ggplot() +
    aes(x = rewCond, group = alt, y = RT, color = alt) +
    geom_line(size=1) +  
    scale_linetype_manual(values=c("solid", "solid"))+
    geom_text(aes(y = RT, label = round(RT)), position=position_dodge(width=0.6), size = 5.5)+
    geom_point(size=3, fill="white") +         
    geom_errorbar(data=sum, mapping=aes(x=rewCond, ymin=RT-se, ymax=RT+se), width=0.1, size=.7, color="black", position=position_dodge(width=0.0)) +
    scale_color_manual(values=cbPalette) +
    theme_hc(base_size = 17, base_family = "sans", style = c("default", "darkunica")) +
    theme(
      axis.title.y = element_text(vjust= 1.8, size = 18),
      axis.title.x = element_text(vjust= -0.5, face="bold.italic", size = 18),
      axis.title = element_text(face = "bold"),
      plot.title = element_text(color="black", size=16, face="bold.italic"),
      axis.text=element_text(size=15, face = "bold"),
      legend.position = c(0.9, 0.2),
      legend.background = element_rect(fill="lightblue",
                                       size=0.5, linetype="solid", 
                                       colour ="darkblue"),
      legend.title = element_text(colour="black", size=15, face="bold")) )
plotH+ scale_y_continuous(breaks=seq(600:640*10)) #increment y-axis marker by 10
plotH+labs(title="EEG-ET: Effect of Task: F(1,41) = 17.01, p <.001 \n Effect of Reward Condition: F(1,41) = 34.7, p <.001 \n
           Interaction was non-significant", 
           x="Reward Condition", y = "Reaction Time in Milliseconds") 

```


